On Secure Delegation of SampBQP with a Classical Client

### 2020-04-05 qpip.tex
Remove another done author note

\begin{thm}
    \label{QPIP1thm}
	$\PiSamp$ has negligible completeness error and $O(\varepsilon)$ soundness error.
\end{thm}
\begin{prf}
	For completeness, notice $z_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
	So we can apply Chernoff bound (\Cref{thm:Chernoff}) \Ethan{Theorem numbering needs fix} with $\mu=\frac{m}{2}$ and $\delta=\frac{c\varepsilon^2}{\left(T+\frac{T}{\varepsilon}\right)^5}$ to get
	$$\Prob{Z>\frac{m}{2}-\varepsilon m}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(\varepsilon^{-1}).$$

>>>>

\begin{thm}
    \label{QPIP1thm}
	$\PiSamp$ has negligible completeness error and $O(\varepsilon)$ soundness error.
\end{thm}
\begin{prf}
	For completeness, notice $z_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
	So we can apply Chernoff bound (\Cref{thm:Chernoff}) with $\mu=\frac{m}{2}$ and $\delta=\frac{c\varepsilon^2}{\left(T+\frac{T}{\varepsilon}\right)^5}$ to get
	$$\Prob{Z>\frac{m}{2}-\varepsilon m}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(\varepsilon^{-1}).$$
